\Rpackage{MSnbase} development

### 2011-09-20 inst/doc/Foreword.tex
fixed typo in vignette foreword
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@55303 bc3139a8-67e5-0310-9ffc-ced21a209358
Spectrum2 ms1scan slot updated to precScanNum, using mzR::header()$precursorScanNum to populate. Updated and exported readIspyData.
 o removed (internal) Mascot query link column in readIspyData 
   to work with latest ouput version <2011-09-12 Mon>
 o removed the fillUp part in readIspyData <2011-09-14 Wed>
 o exported readIspyData <2011-09-20 Tue>
 o removed link to proteomics sig list <2011-09-20 Tue>
 o removed url in DESCRIPTION <2011-0

>>>>

\bigskip

You are welcome to contact me for questions, bugs, typos or suggestions about \Rpackage{MSnbase}. 
If you wish to reach a broader audience for general questions about proteomics analysis using \texttt{R}, 
you may want to use the Bioconductor mailing 
list\footnote{\url{https://stat.ethz.ch/mailman/listinfo/bioconductor}}.
%% proteomics special interest 
%% group\footnote{\url{https://stat.ethz.ch/mailman/listinfo/bioc-sig-proteomics}}.
